\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-28 paper/algorithm.tex

>>>>

\todobox{jose rewrite this clearly}{
While $\textsc{Loss}$ is not monotonically increasing in our model, we maintain a collection of sound and complete Pareto frontiers by 
computing these specific to each dirty set. That is to say, that the combination of $\textsc{Loss}(p) \times \textsc{Dirty}(p)$ for some
plan $p$ behaves monotonically, as the dirty-set is strictly decreasing through the application of $\delta, \mu$ operations. 
The final Pareto frontier corresponds to the collection of plans associated with the empty dirty set.}

### 2017-02-28 paper/algorithms/plan-helpers.tex

    \Require{$q$ is a query plan, $G$ is a set of grouping attributes, $A$ is an aggregation function, $C_g$ is a set of attributes which are used in the final plan.}
    \Ensure{A set of plans for grouping \& aggregating with $G$ and $A$.}
    \Function{OptGroupBy}{$q, G, A, C_g$}
    \State $C \gets G \cup \Call{Attrs}{A}$
    \State $Q' \gets \Call{AddImpute}{q, C, C_g}$
    \State \Return $\{\Call{GroupBy}{q', G, A} ~|~ q' \in Q'\}$
    \EndFunction

@@

    \Require{$q$ is a query plan, $P$ is a set of projection attributes.}
    \Ensure{A set of plans with the attributes in $P$ projected.}
    \Function{OptProject}{$q, P$}
    \State \Return $\{\pi_P(q') ~|~ q' \in \Call{AddImpute}{q, P, P}\}$
    \EndFunction

>>>>

    \Require{$q$ is a query plan, $G$ is a set of grouping attributes, $A$ is an aggregation function, $C_g$ is a set of attributes which are used in the final plan.}
    \Ensure{A set of plans for grouping and aggregating with $G$ and $A$.}
    \Function{OptGroupBy}{$q, G, A, C_g$}
    \State $C \gets G \cup \Call{Attrs}{A}$
    \State $Q' \gets \Call{AddImpute}{q, C, C_g}$
    \State \Return $\{\Call{GroupBy}{q', G, A} ~|~ q' \in Q'\}$
    \EndFunction

@@

    \Require{$q$ is a query plan, $P$ is a set of attributes to be projected at the top of the plan.}
    \Ensure{A set of plans with the attributes in $P$ projected.}
    \Function{OptProject}{$q, P$}
    \State \Return $\{\pi_P(q') ~|~ q' \in \Call{AddImpute}{q, P, P}\}$
    \EndFunction

### 2017-02-28 paper/algorithms/plan-toplevel.tex

% \begin{algorithm}
\begin{algorithmic}[1]
  \Require{A set of tables $T$, a relation $F: T \times \Phi$ between tables and filter predicates, a relation $J : T \times \Psi \times T$ between tables and join predicates, a set of projection attributes $P$,  an optional set of grouping attributes $G$ and aggregator function $A$, and a parameter $\alpha \in [0, 1]$ that expresses trade-off performance and information lost}
  \Ensure{An optimized query plan.}

>>>>

% \begin{algorithm}
\begin{algorithmic}[1]
  \Require{A set of tables $T$, a relation $F: T \times \Phi$ between tables and filter predicates, a relation $J : T \times \Psi \times T$ between tables and join predicates, a set of projection attributes $P$,  an optional set of grouping attributes $G$ and aggregator function $A$, and a parameter $\alpha \in [0, 1]$ that expresses the trade-off between performance and imputation quality.}
  \Ensure{An optimized query plan.}
